---
title: "Lwarrell_FinalHomeworkCode_05"
output: html_document
date: "2025-04-13"
---

## [1] Using the “KamilarAndCooperData.csv” dataset, run a linear regression looking at log(HomeRange_km2) in relation to log(Body_mass_female_mean) and report your $\beta$ coeffiecients (slope and intercept).

### Let's Begin by loading our data in!

```{r}
library(curl)
f<-curl("https://raw.githubusercontent.com/fuzzyatelin/fuzzyatelin.github.io/refs/heads/master/AN588_Spring25/KamilarAndCooperData.csv")
k<-read.csv(f)
```

### Let's take a look at this data.

```{r}
head(k)
str(k)
```

### Our goal is to run a linear regression between the log of HomeRange_km2 and the log of Body_mass_female_mean so let's see what we find!

```{r}
lmHB<-lm(data=k, log(HomeRange_km2)~log(Body_mass_female_mean)) #our linear regression equation
summary(lmHB) #B0 and B1 are the estimate intercept and estimate log(Body_mass_female_mean)
```

### **Our $\beta$ 0 (or y-intercept) is -9.44123 and our $\beta$ 1 (or slope) is 1.03643. For later comparison, let's also extract our original CIs!**


```{r}
CIHB<-confint(lmHB, level=.95) #just pulls our CIs from the linear regression
CIHB
```

## [2] Then, use bootstrapping to sample from your data 1000 times with replacement, each time fitting the same model and calculating the same coefficients. This generates a sampling distribution for each $\beta$ coefficient.

### Let's begin our bootstrap

```{r}
nHB<-1000 #we want 1000 samples
coefsHB<-matrix(NA, nrow=nHB, ncol=length(coef(lmHB))) #pulling our coefs into a matrix to make them easier to sort through later
colnames(coefsHB)<-names(coef(lmHB)) #naming our columns :)
for (i in 1:nHB) {
  sHB<-k[sample(nrow(k),replace=T),] #sampling for our bootstrapping
  blmHB<-lm(data=sHB, log(HomeRange_km2)~log(Body_mass_female_mean)) #linear regression for the bootsrap
  coefsHB[i,]<-coef(blmHB)
}
```

### Now that we have our bootstrap, let's calculate the Standard Error and CI

```{r}
# Calculate bootstrap SEs
boot_SE <- apply(coefsHB, 2, sd)

# Calculate 95% CI using percentiles
boot_CI <- apply(coefsHB, 2, quantile, probs = c(0.025, 0.975))

boot_SE
boot_CI
```

```{r}
summary(blmHB)
confint(blmHB)
```

```{r}
# Model-based SEs
summary(lmHB)$coefficients[, "Std. Error"]

# Model-based CIs
confint(lmHB)

# Then compare with boot_SE and boot_CI above
```

```{r}
#direct print out of the SE and CI from what you have calculated above 

cat("Bootstrap SEs:\n")
print(round(boot_SE, 4))

cat("Bootstrap 95% CIs:\n")
print(round(boot_CI, 4))
```

```{r}
summary(lmHB)
CIHB
```
Our $\beta$ 0 SE was .67293 and our $\beta$ 1 SE was .08488 which is similar but not identical to our bootstrap results. Our $\beta$ 0 CIs were -10.7720889 and -8.110374 while our $\beta$ 1 CIs were .8685707 and 1.204292 which are identical to our bootstap results!

